---
title: "Extracting World Poll data for replication file we can share"
author: "Erik Ø. Sørensen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("haven")
```

# Data availability policy

There are no restrictions on the data used that were collected as part
of the Fairness-Across-the-World module; these outcomes will be publicly
released with a core set of individual background variables. The
remaining set of background variables will be made available upon
request (in order to secure the privacy of individual respondents).

## Gallup policy on what respondent level data can be shared openly:

From Zacc Ritter (Gallup), March 8 2021:

> For general public release, we ask our clients to limit the
> demographic/background variables to the following: Weights (wgt),
> country (WP5), gender (WP1219), age (WP1220), education (WP3117),
> income (INCOME_2), and urbanicity (WP14).
>
> We ask that when NHH makes its 2018 Fairness Around the World data set
> available to the general public, it sticks to this delimited set of
> variables.
>
> In the specific case that another researcher reaches out for a more
> comprehensive data set, Gallup is willing to reach a compromise. NHH
> may provide that specific researcher the more extensive list of
> variables specified below. We ask that NHH not release any of other
> respondent-level items to that researcher not specified below.
>
> 1.  SURVEY STRUCTURE: Weights (wgt), PSUs (WP12259), and country
>     (WP5).
> 2.  BACKGROUND VARIABLES ON INDIVIDUALS/HOUSEHOLDS: gender (WP1219),
>     age (WP1220), marital status (WP1223), number of children under 15
>     years of age (WP1230), education (WP3117), income (INCOME_2 and
>     HHSIZE), employment status (EMP_2010), whether religion is
>     important (WP119), urbanicity (WP14), and whether they are
>     first-generation immigrants (WP4657)

## Gallup policy on access to World Poll respondent level data for verification purposes

From communication with Zacc Ritter (Gallup), March 9, 2021:

> Access to the World Poll Respondent Level Data will be granted to
> individuals representing academic review boards where necessary for
> the purposes of verification of research undertaken using the Client
> commissioned items and World Poll Respondent Level Data. All
> reasonable alternatives must first be exhausted with the reviewing
> body, such as the sharing of topline data. The researcher and Client's
> Project Manager must notify Gallup in writing of such a requirement
> including a copy of the correspondence from the reviewing body. Upon
> such a request Gallup will grant the reviewer access to the data for a
> limited duration for the sole purpose of review.

# Extracting public subset

```{r}
WP_selfishness_public <- readRDS(here::here("data","WP_analytical.rds")) %>%
  filter(in_experiment==TRUE) %>%
  dplyr::select(iso_a3, # Recoding of WP5 
                wgt, # Population weights
                more_selfish, # From Fairness Across the World module
                more_criminal, # From Fairness Across the World module
                gov_should_reduce_inequality, #From Fairness Across the World module
                inequality_unfair, # From Fairness Across the World module
                WP1219, WP1220, WP3117, income_2, WP14) # Core Gallup World Poll variables
saveRDS(WP_selfishness_public, file=here::here("pnas_BSRI/data/WP_selfishness_public.rds"))
write_dta(WP_selfishness_public, here::here("pnas_BSRI/data/WP_selfishness_public.dta"))
write_csv(WP_selfishness_public, file=here::here("pnas_BSRI/data/WP_selfishness_public.csv"))
```

# Session Info

```{r}
sessionInfo()
```
